\documentclass[11pt]{article}

% imports
\usepackage{setspace}
\usepackage{anyfontsize}
\usepackage{enumitem}
\usepackage{xfrac}

% title macros (overriding \section was a pain, so we have custom ones)
\newcommand{\ctitle}[1]{{\fontsize{24}{30} \selectfont \textbf{#1} \par}}
\newcommand{\preamble}[0]{\vskip 11pt \noindent \textbf{\underline{Preamble}}\newline}
\newcounter{articlect}
\newcounter{sectionct}[articlect]
\newcommand{\carticle}[1]{\stepcounter{articlect} \vskip 11pt \noindent \textbf{\underline{\smash{Article \Roman{articlect} - #1}}}\par}
\newcommand{\csection}[0]{\stepcounter{sectionct} \noindent \textbf{Section \arabic{sectionct}. }}
\newcommand{\csectionskip}[0]{\vskip 11pt}

% no para indent
\setlength\parindent{0pt}

% set list spacing and properties
\setlist[enumerate]{noitemsep,nolistsep}
\renewcommand{\theenumi}{\Alph{enumi}}

\begin{document}

% Title header
\begin{center}
\ctitle{Constitution for the RoboJackets at Georgia Tech}

Created 1999 \\
Revised 04/13/2022
\end{center}

% Preamble
\preamble
The RoboJackets competitive robotics club will be one that designs robots with the intent of taking part in various national and international competitions. The purpose of the club is to promote robotics in the Georgia Tech community and to help students learn valuable skills associated with building robots. As a byproduct of taking part in competitions, Georgia Tech will benefit by becoming more familiar to the people in the robotics community. 

% Articles
\carticle{Name}
This organization will be known as RoboJackets at Georgia Tech, hereafter referred to as RoboJackets. 

\carticle{Purpose}
The purpose of the RoboJackets is to: 
\begin{enumerate}
\item Compete in robotics competitions.
\item Promote robotics in the Georgia Tech community.
\item Promote Georgia Tech in the robotics community. 
\item Give students an added outlet for obtaining skills vital to their education.
\item Add value to the surrounding community by way of community projects involving robotics. 
\end{enumerate}

\carticle{Membership}
\begin{enumerate}
\item Eligibility for membership in RoboJackets is extended to all Georgia Tech students who meet eligibility requirements for participation in extracurricular activities as stated in the GT Catalog and SGA policies. Only active Georgia Tech student members in good academic standing can vote or hold office. 
\item Active membership is defined as attending at least one (1) general meeting per semester and attending at least fifty (50) percent of the meetings of one (1) or more project teams.
\item A limit on the maximum number of members will not be set.
\item Membership will take effect when an interested person pays dues for the semester. 
\end{enumerate}

\carticle{Officers}
\csection
According to the GT Catalog, students can only run for, and hold office if they are in good standing with the Institute (academically and non-academically). RoboJackets will further require Officers and officer candidates to be students that have been members of the organization for at least one (1) semester of active membership.
\csectionskip

\csection
An Executive Board comprised of Officers will govern the activities of the organization, and the specific duties of the Officers will be as follows: 
\begin{enumerate}
\item President: The President will have general supervision of the affairs of the RoboJackets and will preside at meetings. The President will approve projects for the organization to be involved in, actively seek projects for the organization, and act as a liaison for companies that wish to support the club.
\item Vice President: The Vice President will be the junior executive officer and will act on the behalf of the President in the event of their absence. The Vice President will work with project managers to ensure projects are executed as planned, and assist in presidential duties.
\item Treasurer: The Treasurer will be responsible for keeping accurate records of the incoming and outgoing expenses from the organization’s accounts, and for creating financial reports that detail the organization’s budget for active and potential sponsors. The treasurer will have final authority to approve all orders.
\item Secretary: The Secretary will be responsible for tracking membership, taking meeting attendance for non-­project specific meetings, and keeping meeting minutes for officer meetings.
\item Shop Manager: The Shop Manager will be responsible for ensuring cleanliness and organization within the shop and will submit requests for shop consumables and capital expenditures to the Treasurer as necessary.
\item Promotions Chair: The Promotions Chair will organize promotions of the RoboJackets in the Georgia Tech community, organize programs that involving helping the surrounding community, and be responsible for creating the guidelines for groups attending competitions to best promote Georgia Tech in the robotics community.
\item Project Managers: The Project Managers will be voted on by the project team members and subject to the approval of the President. They will be responsible for organizing the organization's members that choose to participate in their project. They will prepare budgets to be submitted to the Treasurer for their project and will meet with the aforementioned officers of the organization when requested. 
\end{enumerate}
\csectionskip

The officers of the RoboJackets shall have the power to create or destroy positions of office as is necessary to run an efficient club. 

\carticle{Officer Elections}
Officers will be selected whenever a position needs to be filled or a new position is created. Officer candidates must meet the requirements established in Article IV, Section 1. Elections will be conducted as follows: 
\begin{enumerate}
\item All organization members must be notified at least one (1) week in advance of the start of acceptance of nominations for a new officer.
\item Elections will be held no later than one month before the start of finals.
\item Nominations will be made in a club-wide advertised meeting or through an online nominations form.
\item Nominated candidates will give a short presentation detailing why they wish to hold the position in question, why they are qualified for the position, and how they would fulfill the requirements of the position. Any eligible member may campaign or be nominated for any officer position. 
\item The candidates will leave the room for private discussion by the present club members. The highest ­ranking officer will organize the private discussions by recognizing those members who wish to be heard.
\item After a motion to vote is called and seconded, the present members will each cast one vote for the position being voted on.
\item The candidate receiving a plurality of votes will be elected to the officer position. In the case of a tie vote, the highest­ ranking officer present will cast the deciding vote.
\item New officers take office at the last meeting of the spring semester and remain in office until the next election.
\item If a position remains unfilled after the elections process, the incoming President will appoint a member to the position or reassign duties to another officer.
\end{enumerate}

\carticle{Officer Removal}
\begin{enumerate}
\item If an officer fails to maintain Institute requirements as stated in the GT Catalog and Article 4 Section 1, they shall resign immediately.
\item An officer can be removed from office by \sfrac{2}{3} vote of the full membership of the club or executive board.
\item The meeting for the removal of an officer is called for by a majority vote when quorum is present.
\item The meeting for the removal of an officer must be announced no less than one week in advance.
\item The officer pending removal will be allowed to speak to defend their actions. 
\item The remaining leadership must make a good faith effort to contact the officer and schedule the meeting so that they can attend if desired.
\item If an officer is removed, their removal is immediate. Upon removal, a special election will be held following the rules established for yearly elections in Article V. 
\item If the highest level officer(s) are removed, the next highest officer will assume interim responsibility until the special election is concluded.
\end{enumerate}

\carticle{Member Removal}
\begin{enumerate}
\item Membership of any kind, including specific privileges, can be revoked for failure to maintain membership requirements as stated in this Constitution. The Organization must strive to maintain the highest levels of objectivity in both setting membership requirements and in removing a Member.
\item If it is believed that a Member has failed to maintain membership requirements, then a petition requesting a membership review must be signed by at least half of the voting membership or Executive Board and presented at an Executive Board meeting.  Then, upon verification of the validity of the petition, by the Advisor, and, at least two weeks but no more than four weeks from the date of submission, another meeting shall be held at which the grievance will be presented, with both sides having the opportunity to present a case.
\item The decision-making process for member removal must be explicitly outlined in the organization’s meeting minutes.
\item If the membership review reveals that the Member has not maintained the membership requirements, then the Executive Board will 1) place the Member on a probationary status and 2) outline the objective criteria, including a timeline no shorter than 2 business weeks (no greater than one academic semester), the Member must meet to remove the probationary status.
\begin{enumerate}
\item The Executive Board and the member must agree on the probationary timeline.
\item The timeline must allow feasibility for the infraction to be remedied.
\end{enumerate}
\item If at least 2/3 of the Executive Board votes to place the Member under probationary status, they must publicize their decision to the organization via an electronic means and notify the Advisor.
\item If the Member requests privacy regarding the membership removal process, the Executive Board will not notify the organization of probationary status.
\item At the end of the probationary period, the Executive Board will meet with the Member to determine if the criteria to remove probationary status have been met. If 2/3 of the Executive Board votes that the criteria still have not been met, then the member shall be removed.
\item If the Member is removed, the Executive Board will provide written notification of the removal to the Member, the Organization, and the Advisor indicating the reason for removal and the timeline for application for new membership (if applicable).
\item If the Member is removed, they may appeal to the General Body of the organization within 2 business weeks. The appeal will be provided to the Executive Board and distributed to the general body by the Secretary. The appeal will follow the same procedures as listed in this article, and the General Body will act as the voting body.
\end{enumerate}

\carticle{Committees}
Committees may be created as necessary by the President for specific events and projects not to last longer than the current officer term.
\begin{enumerate}
\item Each committee will have a chair, as appointed by the President.
\item Any member or officer may be selected as a committee chair.
\item Any number of members may be on a committee. 
\end{enumerate}

\carticle{Advisor}
\begin{enumerate}
\item A full-time salaried GT faculty or staff member will serve as Advisor to the organization.
\item Nominations for Advisor will take place within the Executive Board. An Advisor will be chosen within two weeks of a vacancy. The organization will notify the Center for Student Engagement of the new Advisor immediately upon installment. The Executive Board will choose the Advisor by a majority vote and invite them to serve as Advisor for the next academic year.
\item During officer elections, the organization will vote on whether to continue the Advisor appointment or not. The vote must be a majority of those voting in order to retain the Advisor for the next academic year.
\item The duties of Advisor include meeting with organization officers, reviewing the yearly budget, signing all required paperwork, and advising on issues of risk management, organization leadership, and Georgia Tech policy.
\item The Advisor can be removed for not carrying out the duties and expectations as defined in this document. Any member can bring concerns to the Executive Board. The Executive Board will meet with the Advisor to discuss the concerns. After this meeting, the Executive Board will vote on whether to remove the Advisor. If there is a majority vote, then the Advisor will be removed.
\item If an Advisor steps down, is removed, or is not re-appointed, the Executive Board will follow the process stated in Article IX Section B.
\end{enumerate}

\carticle{Dues}
Dues shall be collected by the President, Vice President, Treasurer, and Project Managers. Late dues will be accepted at the discretion of the aforementioned officers. The Treasurer will set the due date for each semester's dues. The Treasurer may entitle delegates to collect dues if the demand requires it. Dues will be set according to our bylaws. Members over the summer semester must have paid for the previous or upcoming year. 

\carticle{Parliamentary Procedure}
All officer/business meetings shall be governed by the procedure contained in Robert’s Rules of Order. 

\vspace{5mm}

Robert's Rules of Order will be used in instances not covered in this constitution. 

\carticle{Non-Discrimination Statement}
Membership and all privileges, including voting and officer positions, must be extended to all students without regard to race, color, sex, sexual orientation, gender identity, gender expression, ethnicity or national origin, religion, age, genetic information, disability, or veteran status, unless exempt under Title IX.   

\carticle{Affiliation}

This organization is a Registered Student Organization (RSO) at Georgia Institute of Technology but is not a part of the Institute itself.
\begin{enumerate}
\item In all correspondence and publications, it may refer to itself as an organization at Georgia Institute of Technology, but not as a part of Georgia Tech itself.
\item RoboJackets accepts full financial and production responsibility for all activities it sponsors.
\item RoboJackets agrees to abide by all pertinent GT policies and regulations. Where GT policies and regulations and those of RSO differ, including those regulations and policies mandated by an external affiliated organization, the policies and regulations of GT take precedence.
\item RoboJackets recognizes and understands that Georgia Tech assumes no legal liability for the actions of the organization.
\end{enumerate}

\carticle{Constitutional Amendments}
Written notification to all members must be made by mail or email, at least two (2) weeks in advance of any proposed change in the constitution. Amendments are subject to the approval by the Student Government and Student Activities Committee. The procedure for amending the constitution is as follows: The amendment will be read in a general meeting open to all club members. All club officers must be in attendance. Once the amendment is read to all members in attendance, an open discussion will ensue. The club president will moderate the discussion. Once all discussion is complete, the members in attendance will vote on whether to accept or deny the amendment. 

\vspace{5mm}

Acceptance of any amendment to the constitution will require \sfrac{2}{3} vote with quorum established. A quorum is established by greater than half of the voting membership.

\vspace{5mm}

Amendments are subject to the approval of the Student Government Association and the Student Activities Committee.

\carticle{External Affiliations}

RoboJackets is affiliated with RoboJackets, Inc., a Georgia non-profit corporation.

\end{document}
